The {TestIdeals} package for \emph{Macaulay2}

### 2019-04-24 Fsing/TestIdealsPaper/TestIdeals.tex
Several small changes in formatting

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z];
i2 : I = ideal( x^6*y*z + x^2*y^12*z^3 + x*y*z^18 );
o2 : Ideal of R
i3 : frobeniusPower( 1/5, I )
                2   3
o3 = ideal (x, y , z )
o3 : Ideal of R
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : S = ZZ/5[x,y,z];
i2 : f = x^3 + y^3 + z^3;
i3 : u = f^(5-1);
i4 : frobeniusRoot( 1, ideal u )
o4 = ideal (z, y, x)
o4 : Ideal of S

i5 : S = ZZ/7[x,y,z];
i6 : f = x^3 + y^3 + z^3;
i7 : u = f^(7-1)
i8 : frobeniusRoot( 1, ideal u )
o8 = ideal 1
o8 : Ideal of S
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : p = 3;
i2 : R = ZZ/p[x,y];
i3 : m = monomialIdeal( x, y );
o3 : MonomialIdeal of R
i4 : I = m^5;
o4 : MonomialIdeal of R
i5 : t = 3/5 - 1/(5*p^3);
i6 : frobeniusPower( t, I )
             2        2
o6 = ideal (y , x*y, x )
o6 : Ideal of R
i7 : frobeniusPower( t - 1/p^5, I )
o7 = ideal (y, x)
o7 : Ideal of R
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i8 : S = ZZ/3[a..f,x,y];
i9 : G = a*x^5 + b*x^4*y + c*x^3*y^2 + d*x^2*y^3 + e*x*y^4 + f*y^5;
i10 : testIdeal( t, G )
              2        2
o10 = ideal (y , x*y, x )
o10 : Ideal of S
i11 : testIdeal( t - 1/p^5, G )
o11 = ideal (y, x)
o11 : Ideal of S
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : p = 2;
i2 : R = ZZ/p[a,b,c,d];
i3 : I = intersect(ideal(a,b),ideal(a,c),ideal(c,d),ideal(c+d,a^3+b*d^2));
o3 : Ideal of R
i4 : f = inducedMap( R^1/I, R^1/frobenius(I) );
o4 : Matrix
i5 : E2 = Ext^2( f, R^1 )
o5 = {-8}  | a4+abc2+abcd a2b            |
     {-10} | a2cd3        a3cd+a3d2+bcd3 |
o5 : Matrix
i6 : target E2
o6 = cokernel {-8}  | 0     a2 b2c2 |
              {-10} | c2+d2 d4 a4d2 |
                            2
o6 : R-module, quotient of R
i7 : source E2
o7 = cokernel {-4} | 0   a  bc  |
              {-5} | c+d d2 a2d |
                            2
o7 : R-module, quotient of R
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i8 : U = matrix entries E2;
             2       2
o8 : Matrix R  <--- R
i9 : A = matrix entries relations source E2;
             2       3
o9 : Matrix R  <--- R
i10 : frobeniusRoot( 1, U )
o10 = {-2} | 1 0 0 |
      {0}  | 0 d a |
              2       3
o10 : Matrix R  <--- R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i11 : V = ascendModule( 1, A, U )
o11 = | 0   a  bc  |
      | c+d d2 a2d |
              2       3
o11 : Matrix R  <--- R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/ideal( x^3 + y^3 + z^3 );
i2 : isFInjective R
o2 = true
i3 : R = ZZ/5[x,y,z]/ideal( x^3 + y^3 + z^3 );
i4 : isFInjective R
o4 = false
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/ideal( (x-1)^5 + (y+1)^5 + z^5 );
i2 : isFInjective R -- R is not globally F-injective...
o2 = false
i3 : isFInjective( R, IsLocal => true ) -- but is F-injective at the origin
o3 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/ideal( x^2 + y*z );
i2 : isFRegular R
o2 = true
i3 : R = ZZ/7[x,y,z]/ideal( x^3 + y^3 + z^3 );
i4 : isFRegular R
o4 = false
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y];
i2 : f = y^2 - x^3;
i3 : isFRegular( 1/2, f )
o3 = true
i4 : isFRegular( 5/6, f )
o4 = false
i5 : isFRegular( 4/5, f )
o5 = false
i6 : isFRegular( 4/5 - 1/100000, f )
o6 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/ideal( (x-1)^3 + (y+1)^3 + z^3 );
i2 : isFRegular R -- R is not globally F-regular...
o2 = false
i3 : isFRegular( R, IsLocal => true ) -- but is F-regular at the origin
o3 = true
i4 : R = ZZ/13[x,y];
i5 : f = (y-2)^2 - (x-3)^3;
i6 : isFRegular( 5/6, f ) -- (R,f^(5/6)) is not F-regular...
o6 = false
i7 : isFRegular( 5/6, f, IsLocal => true ) -- but is F-regular at the origin
o7 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/ideal( x^2 + y*z );
i2 : isFPure R
o2 = true
i3 : R = ZZ/7[x,y,z]/ideal( x^3 + y^3 + z^3 );
i4 : isFPure R
o4 = true
i5 : S = ZZ/2[x,y,z];
i5 : isFPure ideal( y^2 - x^3 )
o5 = false
i6 : isFPure ideal( z^2 - x*y*z + x*y^2 + x^2*y )
o6 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : S = ZZ/3[a,b,c,d,t];
i2 : m = 4;
i3 : n = 3;
i4 : M = matrix{ { a^2 + t^m, b, d }, { c, a^2, b^n-d } };
i5 : I = minors( 2, M );
i6 : R = S/I;
i7 : isFRational R
o7 = true
\end{MyVerbatim}
}\medskip

@@

In this section, we explain how to compute parameter test modules, parameter test ideals, test ideals, and HSLG-modules\footnote{HSLG-modules can be used to give a scheme structure to the $F$-injective or $F$-pure locus.}.

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/ideal( x^4 + y^4 + z^4 );
i2 : N = testModule R;
i3 : N#0
             2             2        2
o3 = ideal (z , y*z, x*z, y , x*y, x )
o3 : Ideal of R
i4 : N#1
o4 = ideal 1
o4 : Ideal of R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/ideal( y*z, x*z, x*y );
i2 : N = testModule R;
i3 : N#0
             2   2   2
o3 = ideal (z , y , x )
o3 : Ideal of R
i4 : N#1
o4 = ideal (y - z, x + z)
o4 : Ideal of R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/2[a..e];
i2 : E = matrix { {a,b,b,e}, {d,d,c,a} };
             2       4
o2 : Matrix R  <--- R
i3 : I = minors( 2, E );
o3 : Ideal of R
i4 : S = R/I;
i5 : J = parameterTestIdeal S
o5 = ideal (c + d, b, a)
o5 : Ideal of S
i6 : J = substitute( J, R );
o6 : Ideal of R
i7 : mingens( J+I )
o7 = | c+d b a de |
             1       4
o7 : Matrix R  <--- R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : T = ZZ/7[x,y];
i2 : S = ZZ/7[a,b,c,d];
i3 : f = map( T, S, { x^3, x^2*y, x*y^2, y^3 } );
i4 : I = ker f;
i5 : R = S/I;
i6 : testIdeal R
o6 = ideal 1
o6 : Ideal of R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i7 : toString QGorensteinGenerator( 1, R )
o7 = a^2*b^6*c^12+a^3*b^4*c^13+a^3*b^5*c^11*d+a^4*b^3*c^12*d+a^5*b*c^13*d+b^
     12*c^6*d^2+a^3*b^6*c^9*d^2+a^4*b^4*c^10*d^2+a^5*b^2*c^11*d^2+a^6*c^12*d
     ^2+b^13*c^4*d^3+a*b^11*c^5*d^3+a^2*b^9*c^6*d^3+a^4*b^5*c^8*d^3+a^5*b^3*
     c^9*d^3+a^6*b*c^10*d^3+a*b^12*c^3*d^4+a^2*b^10*c^4*d^4+a^3*b^8*c^5*d^4+
     a^4*b^6*c^6*d^4+a^5*b^4*c^7*d^4+a^6*b^2*c^8*d^4+a^7*c^9*d^4+a*b^13*c*d^
     5+a^2*b^11*c^2*d^5+a^3*b^9*c^3*d^5+a^4*b^7*c^4*d^5+a^5*b^5*c^5*d^5+a^6*
     b^3*c^6*d^5+a^7*b*c^7*d^5+a^2*b^12*d^6+a^3*b^10*c*d^6+a^4*b^8*c^2*d^6+a
     ^5*b^6*c^3*d^6+a^6*b^4*c^4*d^6+a^7*b^2*c^5*d^6+a^8*c^6*d^6+a^4*b^9*d^7+
     a^5*b^7*c*d^7+a^6*b^5*c^2*d^7+a^7*b^3*c^3*d^7+a^8*b*c^4*d^7+a^6*b^6*d^8
     +a^7*b^4*c*d^8+a^8*b^2*c^2*d^8+a^9*c^3*d^8+a^8*b^3*d^9+a^9*b*c*d^9+a^10
     *d^10
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : T = ZZ/3[x,y];
i2 : S = ZZ/3[a,b,c,d];
i3 : f = map( T, S, { x^3, x^2*y, x*y^2, y^3 } );
i4 : I = ker f;
i5 : R = S/I;
i6 : testIdeal R
o6 = ideal 1
o6 : Ideal of R
\end{MyVerbatim}
}\medskip

@@

Again, consider the maps $T^e : \omega_{R^{1/p^e}} \to \omega_R$ we have considered throughout this section.  It is a theorem of Hartshorne-Speiser, Lyubeznik, and Gabber \cite{HartshorneSpeiserLocalCohomologyInCharacteristicP,LyubeznikFModulesApplicationsToLocalCohomology,Gabber.tStruc} that the descending images
\begin{equation}\label{eq: descending images}
\omega_R \supseteq T(\omega_{R^{1/p}}) \supseteq \dots \supseteq T^e(\omega_{R^{1/p^e}}) \supseteq T^{e+1}(\omega_{R^{1/p^{e+1}}}) \supseteq \cdots
\end{equation}
stabilize for $e \gg 0$.
The function \texttt{HSLGModule} computes the stable submodule in this chain, called the \emph{HSLG module}, and returns a list containing the following items:
\begin{enumerate}[(1)]
   \item The HSLG module;
   \item The canonical module, embedded (non-uniquely) as an ideal;
   \item The element $u$ representing the map on the canonical module (see
   \autoref{subsec.DualToFrobeniusOnQuotientRings});
   \item The value of $e > 0$ at which the descending images in \eqref{eq: descending images} stabilize.  This is sometimes also called the HSLG-number of the canonical module as a Cartier module.
\end{enumerate}

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/3[x,y,z]/ideal( x^3 + y^4 + z^5 );
i2 : L = HSLGModule R;
i3 : L#0
                          2        2   3
o3 = ideal (0, y*z, x*z, y , x*y, x , z )
o3 : Ideal of R
i4 : L#1
o4 = ideal 1
o4 : Ideal of R
i5 : L#3
o5 = 1
\end{MyVerbatim}
}\medskip

@@

\begin{definition}
Let $K$ be an $F$--finite field of prime characteristic $p,$ and let
$f\in R=K[x_1,\ldots, x_d].$ We define the \emph{level of} $f$ as the
smallest possible integer $e$ where the descending chain
\[
R=(f^{p^0-1})^{[1/p^0]}\supseteq (f^{p-1})^{[1/p]}\supseteq
(f^{p^2-1})^{[1/p^2]}\supseteq\ldots%\supseteq (f^{p^{i-1}-1})^{[1/p^{i-1}]}
\supseteq (f^{p^i-1})^{[1/p^i]}\supseteq\ldots
\]
stabilizes.
\end{definition}
This invariant was introduced in \cite{AlvarezBlickleLyubeznik2005}.  It is also essentially the same data as the HSLG-number of the pair $(R, f^1)$ as computed in (4) above (it is that number $+1$).
One interesting particular
case is when $K=\mathbb{F}_p$ and $f$ is the defining homogeneous polynomial of a hyperelliptic curve
of genus $g;$ when $g=1,$ it was proved in
\cite{BoixDeStefaniVanzo2015} that the corresponding elliptic curve defined by $f$
is ordinary if and only if its level is $1,$ (equivalently, if and only if
$(R/(f))_{(x,y,z)}$ is $F$--pure, %this was already proved by Takagi and Takahashi in \cite{TakTak08}
) and supersingular if and only if its level is $2.$ When
the genus is at least $2,$ level $2$ is a necessary (but not sufficient) condition for the curve
for being ordinary \cite{BlancoBoixFordhamYilmaz2018}; in this case, one also
has that, if the curve is supersingular, then its level has to be at least $3,$ so the level can
always distinguish these two properties in any genus. We illustrate these results by means
of the following examples.

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/2[x,y,z];
i2 : f = x^3+y^2*z+y*z^2;
i3 : frobeniusPower( 1/2, ideal f )
o3 = ideal (x, y, z)
o3 : Ideal of R
i4 : u=f^3;
i5 : frobeniusPower( 1/4, ideal u )
o6 = ideal (x, y, z)
o6 : Ideal of R
i7 : ((HSLGModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y,z];
i2 : f = y^2*z^3-x^5-2*z^5;
i3 : frobeniusPower( 1/11, ideal f^10 )
             2        3
o6 = ideal (z , x*z, x )
o3 : Ideal of R
i5 : frobeniusPower( 1/121, ideal f^120 )
             2        3
o6 = ideal (z , x*z, x )
o6 : Ideal of R
i7 : ((HSLGModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/2[a..f];
i2 : E = matrix { {a,b,b,e}, {d,d,c,a} };
             2       4
o2 : Matrix R  <--- R
i3 : I = minors( 2, E );
o3 : Ideal of R
i4 : S = R/I;
i5 : isCohenMacaulay S
o5 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i6 : omega = canonicalIdeal S
o6 = ideal (e, d, a)
o6 : Ideal of S
i7 : omega = substitute( omega, R ) + I;
o7 : Ideal of R
i8 : u = intersect( (frobenius I ):I, ( frobenius omega ):omega );
o8 : Ideal of R
i9 : u = compress( (gens u) % gens( frobenius I) )
o9 = | a3bc+a3bd+a2cde+abcde+abd2e+b2d2e+cd2e2+d3e2 |
             1       1
o9 : Matrix R  <--- R
i10 : u = first first entries u
       3       3       2                         2     2 2       2 2    3 2
o10 = a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e
o10 : R
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i11 : L = compatibleIdeals u;
i12 : print \ L;
       3       3       2                         2     2 2       2 2    3 2
ideal(a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
               2
ideal (a + b, a  + d*e)
ideal (d, a)
ideal (d, a, e)
ideal (e, d, a, c)
ideal (e, d, c, b, a)
ideal (e, d, b, a)
ideal (d, a, c)
ideal (d, c, b, a)
ideal (d, b, a)
                      2
ideal (c + d, a + b, b  + d*e)
ideal (c + d, b, a, e)
ideal (b, a, e)
\end{MyVerbatim}
}
\medskip

>>>>

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z];
i2 : I = ideal(x^6*y*z + x^2*y^12*z^3 + x*y*z^18);
o2 : Ideal of R
i3 : frobeniusPower(1/5, I)
                2   3
o3 = ideal (x, y , z )
o3 : Ideal of R
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : S = ZZ/5[x,y,z];
i2 : f = x^3 + y^3 + z^3;
i3 : u = f^(5 - 1);
i4 : frobeniusRoot(1, ideal u)
o4 = ideal (z, y, x)
o4 : Ideal of S

i5 : S = ZZ/7[x,y,z];
i6 : f = x^3 + y^3 + z^3;
i7 : u = f^(7 - 1)
i8 : frobeniusRoot(1, ideal u)
o8 = ideal 1
o8 : Ideal of S
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : p = 3;
i2 : R = ZZ/p[x,y];
i3 : m = monomialIdeal(x, y);
o3 : MonomialIdeal of R
i4 : I = m^5;
o4 : MonomialIdeal of R
i5 : t = 3/5 - 1/(5*p^3);
i6 : frobeniusPower(t, I)
             2        2
o6 = ideal (y , x*y, x )
o6 : Ideal of R
i7 : frobeniusPower(t - 1/p^5, I)
o7 = ideal (y, x)
o7 : Ideal of R
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i8 : S = ZZ/3[a..f,x,y];
i9 : G = a*x^5 + b*x^4*y + c*x^3*y^2 + d*x^2*y^3 + e*x*y^4 + f*y^5;
i10 : testIdeal(t, G)
              2        2
o10 = ideal (y , x*y, x )
o10 : Ideal of S
i11 : testIdeal(t - 1/p^5, G)
o11 = ideal (y, x)
o11 : Ideal of S
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : p = 2;
i2 : R = ZZ/p[a,b,c,d];
i3 : I = intersect(ideal(a, b),ideal(a, c),ideal(c, d),ideal(c + d, a^3 + b*d^2));
o3 : Ideal of R
i4 : f = inducedMap(R^1/I, R^1/frobenius(I));
o4 : Matrix
i5 : E2 = Ext^2(f, R^1)
o5 = {-8}  | a4+abc2+abcd a2b            |
     {-10} | a2cd3        a3cd+a3d2+bcd3 |
o5 : Matrix
i6 : target E2
o6 = cokernel {-8}  | 0     a2 b2c2 |
              {-10} | c2+d2 d4 a4d2 |
                            2
o6 : R-module, quotient of R
i7 : source E2
o7 = cokernel {-4} | 0   a  bc  |
              {-5} | c+d d2 a2d |
                            2
o7 : R-module, quotient of R
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i8 : U = matrix entries E2;
             2       2
o8 : Matrix R  <--- R
i9 : A = matrix entries relations source E2;
             2       3
o9 : Matrix R  <--- R
i10 : frobeniusRoot(1, U)
o10 = {-2} | 1 0 0 |
      {0}  | 0 d a |
              2       3
o10 : Matrix R  <--- R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i11 : V = ascendModule(1, A, U)
o11 = | 0   a  bc  |
      | c+d d2 a2d |
              2       3
o11 : Matrix R  <--- R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);
i2 : isFInjective R
o2 = true
i3 : R = ZZ/5[x,y,z]/(x^3 + y^3 + z^3);
i4 : isFInjective R
o4 = false
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/((x - 1)^5 + (y + 1)^5 + z^5);
i2 : isFInjective R -- R is not globally F-injective...
o2 = false
i3 : isFInjective(R, IsLocal => true) -- but is F-injective at the origin
o3 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(x^2 + y*z);
i2 : isFRegular R
o2 = true
i3 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);
i4 : isFRegular R
o4 = false
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y];
i2 : f = y^2 - x^3;
i3 : isFRegular(1/2, f)
o3 = true
i4 : isFRegular(5/6, f)
o4 = false
i5 : isFRegular(4/5, f)
o5 = false
i6 : isFRegular(4/5 - 1/100000, f)
o6 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/((x - 1)^3 + (y + 1)^3 + z^3);
i2 : isFRegular R -- R is not globally F-regular...
o2 = false
i3 : isFRegular(R, IsLocal => true) -- but is F-regular at the origin
o3 = true
i4 : R = ZZ/13[x,y];
i5 : f = (y - 2)^2 - (x - 3)^3;
i6 : isFRegular(5/6, f) -- (R,f^(5/6)) is not F-regular...
o6 = false
i7 : isFRegular(5/6, f, IsLocal => true) -- but is F-regular at the origin
o7 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(x^2 + y*z);
i2 : isFPure R
o2 = true
i3 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);
i4 : isFPure R
o4 = true
i5 : S = ZZ/2[x,y,z];
i5 : isFPure ideal(y^2 - x^3)
o5 = false
i6 : isFPure ideal(z^2 - x*y*z + x*y^2 + x^2*y)
o6 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : S = ZZ/3[a,b,c,d,t];
i2 : m = 4;
i3 : n = 3;
i4 : M = matrix{{ a^2 + t^m, b, d }, { c, a^2, b^n - d }};
i5 : I = minors(2, M);
i6 : R = S/I;
i7 : isFRational R
o7 = true
\end{MyVerbatim}
}\medskip

@@

In this section, we explain how to compute parameter test modules, parameter test ideals, test ideals, and HSLG modules\footnote{HSLG modules can be used to give a scheme structure to the $F$-injective or $F$-pure locus.}.

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(x^4 + y^4 + z^4);
i2 : N = testModule R;
i3 : N#0
             2             2        2
o3 = ideal (z , y*z, x*z, y , x*y, x )
o3 : Ideal of R
i4 : N#1
o4 = ideal 1
o4 : Ideal of R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(y*z, x*z, x*y);
i2 : N = testModule R;
i3 : N#0
             2   2   2
o3 = ideal (z , y , x )
o3 : Ideal of R
i4 : N#1
o4 = ideal (y - z, x + z)
o4 : Ideal of R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/2[a..e];
i2 : E = matrix {{a, b, b, e}, {d, d, c, a}};
             2       4
o2 : Matrix R  <--- R
i3 : I = minors(2, E);
o3 : Ideal of R
i4 : S = R/I;
i5 : J = parameterTestIdeal S
o5 = ideal (c + d, b, a)
o5 : Ideal of S
i6 : J = substitute(J, R);
o6 : Ideal of R
i7 : mingens(J + I)
o7 = | c+d b a de |
             1       4
o7 : Matrix R  <--- R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : T = ZZ/7[x,y];
i2 : S = ZZ/7[a,b,c,d];
i3 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});
i4 : I = ker f;
i5 : R = S/I;
i6 : testIdeal R
o6 = ideal 1
o6 : Ideal of R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i7 : toString QGorensteinGenerator(1, R)
o7 = a^2*b^6*c^12+a^3*b^4*c^13+a^3*b^5*c^11*d+a^4*b^3*c^12*d+a^5*b*c^13*d+b^
     12*c^6*d^2+a^3*b^6*c^9*d^2+a^4*b^4*c^10*d^2+a^5*b^2*c^11*d^2+a^6*c^12*d
     ^2+b^13*c^4*d^3+a*b^11*c^5*d^3+a^2*b^9*c^6*d^3+a^4*b^5*c^8*d^3+a^5*b^3*
     c^9*d^3+a^6*b*c^10*d^3+a*b^12*c^3*d^4+a^2*b^10*c^4*d^4+a^3*b^8*c^5*d^4+
     a^4*b^6*c^6*d^4+a^5*b^4*c^7*d^4+a^6*b^2*c^8*d^4+a^7*c^9*d^4+a*b^13*c*d^
     5+a^2*b^11*c^2*d^5+a^3*b^9*c^3*d^5+a^4*b^7*c^4*d^5+a^5*b^5*c^5*d^5+a^6*
     b^3*c^6*d^5+a^7*b*c^7*d^5+a^2*b^12*d^6+a^3*b^10*c*d^6+a^4*b^8*c^2*d^6+a
     ^5*b^6*c^3*d^6+a^6*b^4*c^4*d^6+a^7*b^2*c^5*d^6+a^8*c^6*d^6+a^4*b^9*d^7+
     a^5*b^7*c*d^7+a^6*b^5*c^2*d^7+a^7*b^3*c^3*d^7+a^8*b*c^4*d^7+a^6*b^6*d^8
     +a^7*b^4*c*d^8+a^8*b^2*c^2*d^8+a^9*c^3*d^8+a^8*b^3*d^9+a^9*b*c*d^9+a^10
     *d^10
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : T = ZZ/3[x,y];
i2 : S = ZZ/3[a,b,c,d];
i3 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});
i4 : I = ker f;
i5 : R = S/I;
i6 : testIdeal R
o6 = ideal 1
o6 : Ideal of R
\end{MyVerbatim}
}\medskip

@@

Again, consider the maps $T^e : \omega_{R^{1/p^e}} \to \omega_R$ we have considered throughout this section.  It is a theorem of Hartshorne-Speiser, Lyubeznik, and Gabber \cite{HartshorneSpeiserLocalCohomologyInCharacteristicP,LyubeznikFModulesApplicationsToLocalCohomology,Gabber.tStruc} that the descending images
\begin{equation}\label{eq: descending images}
\omega_R \supseteq T(\omega_{R^{1/p}}) \supseteq \dots \supseteq T^e(\omega_{R^{1/p^e}}) \supseteq T^{e+1}(\omega_{R^{1/p^{e+1}}}) \supseteq \cdots
\end{equation}
stabilize for $e \gg 0$.
The function \texttt{HSLGModule} computes the stable submodule in this chain, called the \emph{HSLG module}, and returns a list containing the following items:
\begin{enumerate}[(1)]
   \item The HSLGmodule;
   \item The canonical module, embedded (non-uniquely) as an ideal;
   \item The element $u$ representing the map on the canonical module (see
   \autoref{subsec.DualToFrobeniusOnQuotientRings});
   \item The value of $e > 0$ at which the descending images in \eqref{eq: descending images} stabilize.  This is sometimes also called the HSLG number of the canonical module as a Cartier module.
\end{enumerate}

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/3[x,y,z]/(x^3 + y^4 + z^5);
i2 : L = HSLGModule R;
i3 : L#0
                          2        2   3
o3 = ideal (0, y*z, x*z, y , x*y, x , z )
o3 : Ideal of R
i4 : L#1
o4 = ideal 1
o4 : Ideal of R
i5 : L#3
o5 = 1
\end{MyVerbatim}
}\medskip

@@

\begin{definition}
Let $K$ be an $F$--finite field of prime characteristic $p,$ and let
$f\in R=K[x_1,\ldots, x_d].$ We define the \emph{level of} $f$ as the
smallest possible integer $e$ where the descending chain
\[
R=(f^{p^0-1})^{[1/p^0]}\supseteq (f^{p-1})^{[1/p]}\supseteq
(f^{p^2-1})^{[1/p^2]}\supseteq\ldots%\supseteq (f^{p^{i-1}-1})^{[1/p^{i-1}]}
\supseteq (f^{p^i-1})^{[1/p^i]}\supseteq\ldots
\]
stabilizes.
\end{definition}
This invariant was introduced in \cite{AlvarezBlickleLyubeznik2005}.  It is also essentially the same data as the HSLG number of the pair $(R, f^1)$ as computed in (4) above (it is that number $+1$).
One interesting particular
case is when $K=\mathbb{F}_p$ and $f$ is the defining homogeneous polynomial of a hyperelliptic curve
of genus $g;$ when $g=1,$ it was proved in
\cite{BoixDeStefaniVanzo2015} that the corresponding elliptic curve defined by $f$
is ordinary if and only if its level is $1,$ (equivalently, if and only if
$(R/(f))_{(x,y,z)}$ is $F$--pure, %this was already proved by Takagi and Takahashi in \cite{TakTak08}
) and supersingular if and only if its level is $2.$ When
the genus is at least $2,$ level $2$ is a necessary (but not sufficient) condition for the curve
for being ordinary \cite{BlancoBoixFordhamYilmaz2018}; in this case, one also
has that, if the curve is supersingular, then its level has to be at least $3,$ so the level can
always distinguish these two properties in any genus. We illustrate these results by means
of the following examples.

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/2[x,y,z];
i2 : f = x^3 + y^2*z + y*z^2;
i3 : frobeniusPower(1/2, ideal f)
o3 = ideal (x, y, z)
o3 : Ideal of R
i4 : u=f^3;
i5 : frobeniusPower(1/4, ideal u)
o6 = ideal (x, y, z)
o6 : Ideal of R
i7 : ((HSLGModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/11[x,y,z];
i2 : f = y^2*z^3 - x^5 - 2*z^5;
i3 : frobeniusPower(1/11, ideal f^10)
             2        3
o6 = ideal (z , x*z, x )
o3 : Ideal of R
i5 : frobeniusPower(1/121, ideal f^120)
             2        3
o6 = ideal (z , x*z, x )
o6 : Ideal of R
i7 : ((HSLGModule(1, f))#3) + 1
o7 : 2
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/2[a..f];
i2 : E = matrix {{a, b, b, e}, {d, d, c, a}};
             2       4
o2 : Matrix R  <--- R
i3 : I = minors(2, E);
o3 : Ideal of R
i4 : S = R/I;
i5 : isCohenMacaulay S
o5 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i6 : omega = canonicalIdeal S
o6 = ideal (e, d, a)
o6 : Ideal of S
i7 : omega = substitute(omega, R) + I;
o7 : Ideal of R
i8 : u = intersect((frobenius I):I, (frobenius omega) : omega);
o8 : Ideal of R
i9 : u = compress((gens u) % gens(frobenius I))
o9 = | a3bc+a3bd+a2cde+abcde+abd2e+b2d2e+cd2e2+d3e2 |
             1       1
o9 : Matrix R  <--- R
i10 : u = first first entries u
       3       3       2                         2     2 2       2 2    3 2
o10 = a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e
o10 : R
\end{MyVerbatim}
}
\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i11 : L = compatibleIdeals u;
i12 : print \ L;
        3       3       2                         2     2 2       2 2    3 2
ideal (a b*c + a b*d + a c*d*e + a*b*c*d*e + a*b*d e + b d e + c*d e  + d e )
               2
ideal (a + b, a  + d*e)
ideal (d, a)
ideal (d, a, e)
ideal (e, d, a, c)
ideal (e, d, c, b, a)
ideal (e, d, b, a)
ideal (d, a, c)
ideal (d, c, b, a)
ideal (d, b, a)
                      2
ideal (c + d, a + b, b  + d*e)
ideal (c + d, b, a, e)
ideal (b, a, e)
\end{MyVerbatim}
}
\medskip
